To Do

### 2022-08-26 Summary.Rmd
Update on summary

```{r Show levels Europe, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}
pref = pref %>% 
mutate(Cover_names = fct_recode(as.factor(Cover_names),
#1 Check with Nacho, dehesas and others 
Seminatural = "Agro-forestry areas", #1) 2.4.4 
#2 Check with Nacho 
Urban = "Airports", #2) 1.2.4 
#3 Crops 
Agricultural = "Annual crops associated with permanent crops", #3) 2.4.1 
#4 Very different cover type, not included 
Discard = "Bare rocks", #4) 3.3.2 
#5 Very different cover type, not included 
Discard = "Beaches, dunes, sands", #5) 3.3.1 
#6 Not included, lack of details 
Discard = "Burnt areas", #6 3.3.4
#7 Not included, only water surface
Discard = "Coastal lagoons", #7) 5.2.1 
#8 Straightforward
Natural = "Coniferous forest", #8) 3.1.2
#9 Excluded, complex to consider because it lacks habitat context
Urban = "Construction sites", #9) 1.3.3
#10 Based on the images and the description has a lot of vegetation cover
Urban = "Discontinuous urban fabric", #10) 1.1.2
#11 Pollinators here are likely to depend much on the context not on the dump
Discard = "Dump sites", #11) 1.3.2
#12 Filter out, water body
Discard = "Estuaries", #12) 5.2.2 
#13 Straightforward
Agricultural = "Fruit trees and berry plantations", #13) 2.2.2
#14 Urban as embedded within the city
Urban = "Green urban areas", #14) 1.4.1
#15 Highly modified
Urban = "Industrial or commercial units", #15) 1.2.1
#16 By definion, seminatural
Seminatural = "Land principally occupied by agriculture, with significant areas of natural vegetation", #16) 2.4.3
#17 Discard as is not clear the vegetation context
Discard = "Mineral extraction sites", #17) 1.3.1
#18 Straightforward 3.1.3
Natural = "Mixed forest", #18) 3.1.3
#19 Crystal clear category
Natural = "Moors and heathland", #19) 3.2.2
#20 Crystal clear category
Natural = "Natural grasslands", #20) 3.2.1
#21 Filter out
Discard = "NODATA", #21 
#22 cultivated land
Agricultural = "Non-irrigated arable land", #22) 2.1.1
#23 As it is a monoculture despite some very
Agricultural = "Olive groves", #23) 2.2.3
#24 Crystal clear category
Natural = "Peat bogs", #24) 4.1.2
#25 Crystal clear category
Seminatural = "Permanently irrigated land", #25) 2.1.2
#26 Check with Nacho
Urban = "Port areas", #26) 1.2.3
#27 Check with Nacho
Seminatural = "Road and rail networks and associated land", #27) 1.2.2
#28 Check with Nacho but just only 200 records
Seminatural = "Salines", #28) 4.2.2 
#29 Flowering plant communities 
Natural = "Salt marshes", #29) 4.2.1
#30 Sclerophyllous shrubs and low shrubs
Natural = "Sclerophyllous vegetation", #30) 3.2.3
#31 Discard for now 
Discard = "Sea and ocean", #31) 5.2.3
#32 Areas with sparse vegetation, covering 10-50% of surface 
Natural = "Sparsely vegetated areas", #32) 3.3.3
#33 Check with Nacho 
Seminatural = "Sport and leisure facilities", #33) 1.4.2 
#34 Excluded as it is very general
Discard = "Water bodies", #34) 5.1.2
#35 Excluded as it is very general
Discard = "Water courses" #35 5.1.1 
)) %>% 
filter(!Cover_names == "Discard")

pref %>% 
group_by(Cover_names) %>% 
summarise(Levels = length(Cover_names)) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position")
```

@@

```{r Plotting Europe, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE, out.width="70%"}

data <- read_csv("Data/Europe_data/data_preference_brain_weight_europe.csv")

model1 = read_csv("Data/Europe_data/model_output_preference_brain_weight_europe.csv")

model2 = read_csv("Data/Europe_data/model_output_preference_it_europe.csv")

ggplot(model1, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  data, aes(x = Brain.weight, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Brain weight") +
ggtitle("Europe occurrences")

ggplot(model2, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  data, aes(x = IT, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Intertegular distance") +
ggtitle("Europe occurrences")

@@

 pref %>% 
mutate(cover.names = fct_recode(as.factor(cover.names),
      Discard = "Barren Land", #Very different cover type, not included (MA & JB)
      Agricultural = "Cultivated Crops", #(MA & JB)
      Natural = "Deciduous Forest", #(MA & JB)
      Urban = "Developed, High Intensity", #Greater than 50% of cover (MA & JB) 
      Urban = "Developed, Medium Intensity", #Greater than 50% of cover (MA & JB) 
      Seminatural = "Developed, Low Intensity", #Low urban impact (MA & JB)
      Seminatural = "Developed, Open Space", #Open areas with vegetation (MA & JB)
      Natural = "Emergent Herbaceous Wetlands", #(MA & JB)
      Natural = "Evergreen Forest", #(MA & JB)
      Agricultural = "Hay/Pasture", #Highly managed by humans (MA & JB)
      Natural = "Herbaceous", #See explanation below (MA & JB)
      Natural = "Mixed Forest", #(MA & JB)
      Discard = "Open Water", #Low vegetation and land, not included (MA & JB)
      Natural = "Shrub/Scrub", #Heath classified as natural (MA & JB)
      Natural = "Woody Wetlands")) %>% #(MA & JB)
filter(!cover.names == "Discard") %>%  #Discard these categories classified as "Discard"
#Herbaceous and hay/pasture are classified as two different habitats in NLCD. 
#We merged them because herbaceous areas in our sampling region are always 
#for livestock (Koh et al., 2016).
group_by(cover.names) %>% 
summarise(n_rows = length(cover.names)) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position")

@@

```{r Plotting USA, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE, out.width="70%"}

data <- read_csv("Data/Usa_data/data_preference_brain_weight_usa.csv")

model1 = read_csv("Data/Usa_data/model_output_preference_brain_weight_usa.csv")

model2 = read_csv("Data/Usa_data/model_output_preference_it_usa.csv")

ggplot(model1, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  data, aes(x = Brain.weight, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Brain weight") +
ggtitle("USA occurrences")

ggplot(model2, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  data, aes(x = IT, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Intertegular distance") +
ggtitle("USA occurrences")

@@

>>>>

```{r Show levels Europe, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}
pref1 = pref %>% 
mutate(Cover_names = fct_recode(as.factor(Cover_names),
#1 Check with Nacho, dehesas and others 
Seminatural = "Agro-forestry areas", #1) 2.4.4 
#2 Check with Nacho 
Urban = "Airports", #2) 1.2.4 
#3 Crops 
Agricultural = "Annual crops associated with permanent crops", #3) 2.4.1 
#4 Very different cover type, not included 
Discard = "Bare rocks", #4) 3.3.2 
#5 Very different cover type, not included 
Discard = "Beaches, dunes, sands", #5) 3.3.1 
#6 Not included, lack of details 
Discard = "Burnt areas", #6 3.3.4
#7 Not included, only water surface
Discard = "Coastal lagoons", #7) 5.2.1 
#8 Straightforward
Natural = "Coniferous forest", #8) 3.1.2
#9 Excluded, complex to consider because it lacks habitat context
Urban = "Construction sites", #9) 1.3.3
#10 Based on the images and the description has a lot of vegetation cover
Urban = "Discontinuous urban fabric", #10) 1.1.2
#11 Pollinators here are likely to depend much on the context not on the dump
Discard = "Dump sites", #11) 1.3.2
#12 Filter out, water body
Discard = "Estuaries", #12) 5.2.2 
#13 Straightforward
Agricultural = "Fruit trees and berry plantations", #13) 2.2.2
#14 Urban as embedded within the city
Urban = "Green urban areas", #14) 1.4.1
#15 Highly modified
Urban = "Industrial or commercial units", #15) 1.2.1
#16 By definion, seminatural
Seminatural = "Land principally occupied by agriculture, with significant areas of natural vegetation", #16) 2.4.3
#17 Discard as is not clear the vegetation context
Discard = "Mineral extraction sites", #17) 1.3.1
#18 Straightforward 3.1.3
Natural = "Mixed forest", #18) 3.1.3
#19 Crystal clear category
Natural = "Moors and heathland", #19) 3.2.2
#20 Crystal clear category
Natural = "Natural grasslands", #20) 3.2.1
#21 Filter out
Discard = "NODATA", #21 
#22 cultivated land
Agricultural = "Non-irrigated arable land", #22) 2.1.1
#23 As it is a monoculture despite some very
Agricultural = "Olive groves", #23) 2.2.3
#24 Crystal clear category
Natural = "Peat bogs", #24) 4.1.2
#25 Crystal clear category
Seminatural = "Permanently irrigated land", #25) 2.1.2
#26 Check with Nacho
Urban = "Port areas", #26) 1.2.3
#27 Check with Nacho
Seminatural = "Road and rail networks and associated land", #27) 1.2.2
#28 Check with Nacho but just only 200 records
Seminatural = "Salines", #28) 4.2.2 
#29 Flowering plant communities 
Natural = "Salt marshes", #29) 4.2.1
#30 Sclerophyllous shrubs and low shrubs
Natural = "Sclerophyllous vegetation", #30) 3.2.3
#31 Discard for now 
Discard = "Sea and ocean", #31) 5.2.3
#32 Areas with sparse vegetation, covering 10-50% of surface 
Natural = "Sparsely vegetated areas", #32) 3.3.3
#33 Check with Nacho 
Seminatural = "Sport and leisure facilities", #33) 1.4.2 
#34 Excluded as it is very general
Discard = "Water bodies", #34) 5.1.2
#35 Excluded as it is very general
Discard = "Water courses" #35 5.1.1 
)) %>% 
filter(!Cover_names == "Discard")

pref1 %>% 
group_by(Cover_names) %>% 
summarise(Levels = length(Cover_names)) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position")
```

@@

```{r Plotting Europe, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE, fig.height=8, fig.width=6}

long_data <- read_csv("Data/Europe_data/data_preference_residuals_europe.csv")

model1 = read_csv("Data/Europe_data/model_output_preference_residuals_europe.csv")

model2 = read_csv("Data/Europe_data/model_output_preference_brain_weight_europe.csv")

model3 = read_csv("Data/Europe_data/model_output_preference_it_europe.csv")

p1 = ggplot(model1, aes(x = residuals, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = residuals, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Residuals") + 
ggtitle("Europe")

p2 = ggplot(model2, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = Brain.weight, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Brain weight") +
ggtitle("Europe")

p3 = ggplot(model3, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = IT, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Intertegular distance") +
ggtitle("Europe")

library(patchwork)
p1 / p2 / p3 & plot_layout(guides = "collect")

Now we make more strict land use classifications

```{r Table with restricted levels Europe, echo = FALSE, warning = FALSE, message = FALSE}
library(kableExtra)

pref %>% 
group_by(Cover_names) %>% 
summarise(n_rows = length(Cover_names)) %>% 
filter(!Cover_names=="NODATA") %>% 
rename(Land_use = Cover_names) %>% 
arrange(desc(n_rows)) %>% 
mutate(Cover_names = fct_recode(as.factor(Land_use),
#1 Check with Nacho, dehesas and others 
Discard = "Agro-forestry areas", #1) 2.4.4 
#2 Check with Nacho 
Discard = "Airports", #2) 1.2.4 
#3 Crops 
Agricultural = "Annual crops associated with permanent crops", #3) 2.4.1 
#4 Very different cover type, not included 
Discard = "Bare rocks", #4) 3.3.2 
#5 Very different cover type, not included 
Discard = "Beaches, dunes, sands", #5) 3.3.1 
#6 Not included, lack of details 
Discard = "Burnt areas", #6 3.3.4
#7 Not included, only water surface
Discard = "Coastal lagoons", #7) 5.2.1 
#8 Straightforward
Natural = "Coniferous forest", #8) 3.1.2
#9 Excluded, complex to consider because it lacks habitat context
Discard = "Construction sites", #9) 1.3.3
#10 Based on the images and the description has a lot of vegetation cover
Discard = "Discontinuous urban fabric", #10) 1.1.2
#11 Pollinators here are likely to depend much on the context not on the dump
Discard = "Dump sites", #11) 1.3.2
#12 Filter out, water body
Discard = "Estuaries", #12) 5.2.2 
#13 Straightforward
Agricultural = "Fruit trees and berry plantations", #13) 2.2.2
#14 Urban as embedded within the city
Discard = "Green urban areas", #14) 1.4.1
#15 Highly modified
Urban = "Industrial or commercial units", #15) 1.2.1
#16 By definion, seminatural
Agricultural = "Land principally occupied by agriculture, with significant areas of natural vegetation", #16) 2.4.3
#17 Discard as is not clear the vegetation context
Discard = "Mineral extraction sites", #17) 1.3.1
#18 Straightforward 3.1.3
Natural = "Mixed forest", #18) 3.1.3
#19 Crystal clear category
Discard = "Moors and heathland", #19) 3.2.2
#20 Crystal clear category
Discard = "Natural grasslands", #20) 3.2.1
#21 Filter out
Discard = "NODATA", #21 
#22 cultivated land
Agricultural = "Non-irrigated arable land", #22) 2.1.1
#23 As it is a monoculture despite some very
Discard = "Olive groves", #23) 2.2.3
#24 Crystal clear category
Discard = "Peat bogs", #24) 4.1.2
#25 Crystal clear category
Agricultural = "Permanently irrigated land", #25) 2.1.2
#26 Check with Nacho
Discard = "Port areas", #26) 1.2.3
#27 Check with Nacho
Discard = "Road and rail networks and associated land", #27) 1.2.2
#28 Check with Nacho but just only 200 records
Discard = "Salines", #28) 4.2.2 
#29 Flowering plant communities 
Discard = "Salt marshes", #29) 4.2.1
#30 Sclerophyllous shrubs and low shrubs
Discard = "Sclerophyllous vegetation", #30) 3.2.3
#31 Discard for now 
Discard = "Sea and ocean", #31) 5.2.3
#32 Areas with sparse vegetation, covering 10-50% of surface 
Discard = "Sparsely vegetated areas", #32) 3.3.3
#33 Check with Nacho 
Discard = "Sport and leisure facilities", #33) 1.4.2 
#34 Excluded as it is very general
Discard = "Water bodies", #34) 5.1.2
#35 Excluded as it is very general
Discard = "Water courses" #35 5.1.1 
)) %>%  
kbl() %>% 
kable_styling(font_size = 8,latex_options = "hold_position")

```{r Show levels restricted land use Europe, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}
pref2 = pref %>% 
mutate(Cover_names = fct_recode(as.factor(Cover_names),
#1 Check with Nacho, dehesas and others 
Discard = "Agro-forestry areas", #1) 2.4.4 
#2 Check with Nacho 
Discard = "Airports", #2) 1.2.4 
#3 Crops 
Agricultural = "Annual crops associated with permanent crops", #3) 2.4.1 
#4 Very different cover type, not included 
Discard = "Bare rocks", #4) 3.3.2 
#5 Very different cover type, not included 
Discard = "Beaches, dunes, sands", #5) 3.3.1 
#6 Not included, lack of details 
Discard = "Burnt areas", #6 3.3.4
#7 Not included, only water surface
Discard = "Coastal lagoons", #7) 5.2.1 
#8 Straightforward
Natural = "Coniferous forest", #8) 3.1.2
#9 Excluded, complex to consider because it lacks habitat context
Discard = "Construction sites", #9) 1.3.3
#10 Based on the images and the description has a lot of vegetation cover
Discard = "Discontinuous urban fabric", #10) 1.1.2
#11 Pollinators here are likely to depend much on the context not on the dump
Discard = "Dump sites", #11) 1.3.2
#12 Filter out, water body
Discard = "Estuaries", #12) 5.2.2 
#13 Straightforward
Agricultural = "Fruit trees and berry plantations", #13) 2.2.2
#14 Urban as embedded within the city
Discard = "Green urban areas", #14) 1.4.1
#15 Highly modified
Urban = "Industrial or commercial units", #15) 1.2.1
#16 By definion, seminatural
Agricultural = "Land principally occupied by agriculture, with significant areas of natural vegetation", #16) 2.4.3
#17 Discard as is not clear the vegetation context
Discard = "Mineral extraction sites", #17) 1.3.1
#18 Straightforward 3.1.3
Natural = "Mixed forest", #18) 3.1.3
#19 Crystal clear category
Discard = "Moors and heathland", #19) 3.2.2
#20 Crystal clear category
Discard = "Natural grasslands", #20) 3.2.1
#21 Filter out
Discard = "NODATA", #21 
#22 cultivated land
Agricultural = "Non-irrigated arable land", #22) 2.1.1
#23 As it is a monoculture despite some very
Discard = "Olive groves", #23) 2.2.3
#24 Crystal clear category
Discard = "Peat bogs", #24) 4.1.2
#25 Crystal clear category
Agricultural = "Permanently irrigated land", #25) 2.1.2
#26 Check with Nacho
Discard = "Port areas", #26) 1.2.3
#27 Check with Nacho
Discard = "Road and rail networks and associated land", #27) 1.2.2
#28 Check with Nacho but just only 200 records
Discard = "Salines", #28) 4.2.2 
#29 Flowering plant communities 
Discard = "Salt marshes", #29) 4.2.1
#30 Sclerophyllous shrubs and low shrubs
Discard = "Sclerophyllous vegetation", #30) 3.2.3
#31 Discard for now 
Discard = "Sea and ocean", #31) 5.2.3
#32 Areas with sparse vegetation, covering 10-50% of surface 
Discard = "Sparsely vegetated areas", #32) 3.3.3
#33 Check with Nacho 
Discard = "Sport and leisure facilities", #33) 1.4.2 
#34 Excluded as it is very general
Discard = "Water bodies", #34) 5.1.2
#35 Excluded as it is very general
Discard = "Water courses" #35 5.1.1 
)) %>% 
filter(!Cover_names == "Discard")

pref2 %>% 
group_by(Cover_names) %>% 
summarise(Levels = length(Cover_names)) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position")
```

And we model the data with this categories:

```{r Plotting Europe subset, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE, fig.height=8, fig.width=6}

long_data <- read_csv("Data/Europe_data/data_preference_residuals_europe_subset.csv")

model1 = read_csv("Data/Europe_data/model_output_preference_residuals_europe_subset.csv")

model2 = read_csv("Data/Europe_data/model_output_preference_brain_weight_europe_subset.csv")

model3 = read_csv("Data/Europe_data/model_output_preference_it_europe_subset.csv")

p1 = ggplot(model1, aes(x = residuals, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = residuals, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Residuals") + 
ggtitle("Europe")

p2 = ggplot(model2, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = Brain.weight, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Brain weight") +
ggtitle("Europe")

p3 = ggplot(model3, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = IT, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Intertegular distance") +
ggtitle("Europe")

library(patchwork)
p1 + p2 + p3 + plot_layout(ncol = 1) + plot_layout(guides = "collect")

@@

 pref %>% 
mutate(cover.names = fct_recode(as.factor(cover.names),
      Discard = "Barren Land", #Very different cover type, not included (MA & JB)
      Agricultural = "Cultivated Crops", #(MA & JB)
      Natural = "Deciduous Forest", #(MA & JB)
      Urban = "Developed, High Intensity", #Greater than 50% of cover (MA & JB) 
      Urban = "Developed, Medium Intensity", #Greater than 50% of cover (MA & JB) 
      Seminatural = "Developed, Low Intensity", #Low urban impact (MA & JB)
      Seminatural = "Developed, Open Space", #Open areas with vegetation (MA & JB)
      Natural = "Emergent Herbaceous Wetlands", #(MA & JB)
      Natural = "Evergreen Forest", #(MA & JB)
      Agricultural = "Hay/Pasture", #Highly managed by humans (MA & JB)
      Natural = "Herbaceous", #See explanation below (MA & JB)
      Natural = "Mixed Forest", #(MA & JB)
      Discard = "Open Water", #Low vegetation and land, not included (MA & JB)
      Natural = "Shrub/Scrub", #Heath classified as natural (MA & JB)
      Natural = "Woody Wetlands")) %>% #(MA & JB)
filter(!cover.names == "Discard") %>%  #Discard these categories classified as "Discard"
#Herbaceous and hay/pasture are classified as two different habitats in NLCD. 
#We merged them because herbaceous areas in our sampling region are always 
#for livestock (Koh et al., 2016).
group_by(cover.names) %>% 
summarise(n_rows = length(cover.names)) %>% 
arrange(desc(n_rows)) %>%     
kbl() %>% 
kable_styling(latex_options = "hold_position")

@@

```{r Plotting USA, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE, fig.height=8, fig.width=6}

long_data <- read_csv("Data/Usa_data/data_preference_residuals_usa.csv")

model1 = read_csv("Data/Usa_data/model_output_preference_residuals_usa.csv")

model2 = read_csv("Data/Usa_data/model_output_preference_brain_weight_usa.csv")

model3 = read_csv("Data/Usa_data/model_output_preference_it_usa.csv")

p1 = ggplot(model1, aes(x = residuals, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = residuals, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Residuals") + 
ggtitle("USA")

p2 = ggplot(model2, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = Brain.weight, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Brain weight") +
ggtitle("USA")

p3 = ggplot(model3, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = IT, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Intertegular distance") +
ggtitle("USA")

library(patchwork)
p1 / p2 / p3 & plot_layout(guides = "collect")

@@

Now we make more strict categories of what is Natural, Urban and Agricultural. See below:

```{r Show levels USA subset, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

pref_subset <- read_csv("Data/Usa_data/land_cover_usa.csv.gz") %>% 
    dplyr::select(species, cover.names) %>% 
    mutate_if(is.character,as.factor)

pref_subset %>% 
group_by(cover.names) %>% 
summarise(n_rows = length(cover.names)) %>% 
rename(Land_use = cover.names) %>% 
arrange(desc(n_rows)) %>% 
mutate(Cover_names = fct_recode(as.factor(Land_use),
Discard = "Barren Land", #Very different cover type, not included (MA & JB)
Agricultural = "Cultivated Crops", #(MA & JB)
Natural = "Deciduous Forest", #(MA & JB)
Urban = "Developed, High Intensity", #Greater than 50% of cover (MA & JB) 
Urban = "Developed, Medium Intensity", #Greater than 50% of cover (MA & JB) 
Discard = "Developed, Low Intensity", #Low urban impact (MA & JB)
Discard = "Developed, Open Space", #Open areas with vegetation (MA & JB)
Discard = "Emergent Herbaceous Wetlands", #(MA & JB)
Natural = "Evergreen Forest", #(MA & JB)
Discard = "Hay/Pasture", #Highly managed by humans (MA & JB)
Discard = "Herbaceous", #See explanation below (MA & JB)
Natural = "Mixed Forest", #(MA & JB)
Discard = "Open Water", #Low vegetation and land, not included (MA & JB)
Natural = "Shrub/Scrub", #Heath classified as natural (MA & JB)
Natural = "Woody Wetlands")) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position", font_size = 10)
```

Check number of levels per category:

```{r Show levels USA subset levels, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

 pref_subset %>% 
mutate(cover.names = fct_recode(as.factor(cover.names),
Discard = "Barren Land", #Very different cover type, not included (MA & JB)
Agricultural = "Cultivated Crops", #(MA & JB)
Natural = "Deciduous Forest", #(MA & JB)
Urban = "Developed, High Intensity", #Greater than 50% of cover (MA & JB) 
Urban = "Developed, Medium Intensity", #Greater than 50% of cover (MA & JB) 
Discard = "Developed, Low Intensity", #Low urban impact (MA & JB)
Discard = "Developed, Open Space", #Open areas with vegetation (MA & JB)
Discard = "Emergent Herbaceous Wetlands", #(MA & JB)
Natural = "Evergreen Forest", #(MA & JB)
Discard = "Hay/Pasture", #Highly managed by humans (MA & JB)
Discard = "Herbaceous", #See explanation below (MA & JB)
Natural = "Mixed Forest", #(MA & JB)
Discard = "Open Water", #Low vegetation and land, not included (MA & JB)
Natural = "Shrub/Scrub", #Heath classified as natural (MA & JB)
Natural = "Woody Wetlands")) %>% #(MA & JB)
filter(!cover.names == "Discard") %>% 
group_by(cover.names) %>% 
summarise(n_rows = length(cover.names)) %>% 
arrange(desc(n_rows)) %>%     
kbl() %>% 
kable_styling(latex_options = "hold_position")

And we model the data with this categories:

```{r Plotting USA subset, eval = TRUE, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE, fig.height=8, fig.width=6}

long_data <- read_csv("Data/Usa_data/data_preference_residuals_usa_subset.csv")

model1 = read_csv("Data/Usa_data/model_output_preference_residuals_usa_subset.csv")

model2 = read_csv("Data/Usa_data/model_output_preference_brain_weight_usa_subset.csv")

model3 = read_csv("Data/Usa_data/model_output_preference_it_usa_subset.csv")

p1 = ggplot(model1, aes(x = residuals, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = residuals, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Residuals") + 
ggtitle("USA")

p2 = ggplot(model2, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = Brain.weight, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Brain weight") +
ggtitle("USA")

p3 = ggplot(model3, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = IT, y = (Preference)), shape=21) +
geom_line(aes(color=Habitat)) +
theme_bw() +
ylab("Habitat preference") +
xlab("Intertegular distance") +
ggtitle("USA")

library(patchwork)
p1 + p2 + p3 + plot_layout(ncol = 1) + plot_layout(guides = "collect")
